\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-05-10 foci/paper.tex
blacked out anna's netid

\subsection{Software on the Safeplug}
\begin{table}[!t]
\caption{Software and the corresponding version numbers on the Safeplug.}
\label{versions}
\begin{center}
  \begin{tabular}{|l|c|c|c|}
    \hline
    Safeplug Software & Version & Date & Up To Date\\ \hline
    Linux Kernel & 2.6.31.8 & 2009 & No\\ \hline
    Lighttpd Web Server & 1.4.33 & 2013 & No\\ \hline
    Privoxy Proxy & 3.0.21 & 2013 & Yes\\ \hline
    Tor & 0.2.3.25 & 2012 & No\\ \hline
    Dropbear sshd & v0.52 & 2008 & No\\ \hline
  \end{tabular}
\end{center}
\end{table}

@@

\begin{figure*}
  \centering
  \includegraphics[width=.75\textwidth]{disabletor}
  \caption{Disabling Tor as an RPC attack.}
  \label{disable}
\end{figure*}

>>>>

\subsection{Software on the Safeplug}
\begin{table}[!t]
\caption{Software and the corresponding version numbers on the Safeplug.}
\label{versions}
\begin{center}
  \begin{tabular}{|l|c|c|c|}
    \hline
    Safeplug Software & Version & Date & Up To Date (as of May 2014)\\ \hline
    Linux Kernel & 2.6.31.8 & 2009 & No\\ \hline
    Lighttpd Web Server & 1.4.33 & 2013 & No\\ \hline
    Privoxy Proxy & 3.0.21 & 2013 & Yes\\ \hline
    Tor & 0.2.3.25 & 2012 & No\\ \hline
    Dropbear sshd & v0.52 & 2008 & No\\ \hline
  \end{tabular}
\end{center}
\end{table}

@@

\begin{figure*}
  \centering
  \includegraphics[width=.75\textwidth]{disabletor2}
  \caption{Disabling Tor as an RPC attack.}
  \label{disable}
\end{figure*}
